\begin{dfn}[Adjoint Functors]
  \link{adjoint}
  
  Let $R : \map{\CC}{\DD}{\CAT}{}$.
  Then $R$ is a \emph{right adjoint} when 
  there exists $L : \map{\obj{\DD}}{\obj{\CC}}{}{}$ and 
  $(\eta_X) \in \prod_{X \in \obj{\DD}} \mor{X}{RL(X)}{\DD}$ such that 
  for all $X\in\obj{\DD}$, 
  $(L(X),\eta(X))$ is a universal morphism from $X$ to $R$.
  In this case, $L$ is called the \emph{left adjoint of $R$}.
  \newline 
  
  Dually, let $L : \map{\DD}{\CC}{\CAT}{}$.
  Then $L$ is a \emph{left adjoint} when 
  there exists $R : \map{\obj{\CC}}{\obj{\CC}}{}{}$ and 
  $(\ep_U) \in \prod_{U \in \obj{\CC}} \mor{LR(U)}{U}{\CC}$ such that 
  for all $U\in\obj{\CC}$,
  $(R(U),\ep(U))$ is a universal morphism from $L$ to $U$. 
  In this case, $R$ is called the \emph{right adjoint of $L$}.
\end{dfn}

\begin{dfn}[Product Category]
  \link{product_cat}
  
  Let $\CC, \DD$ be categories. 
  Then the \emph{product category of $\CC, \DD$} is denoted 
  $\CC\times\DD$ and is defined as follows. 
  \begin{enumerate}
    \item $\obj{\CC\times\DD} := \obj{\CC}\times\obj{\DD}$.
    \item For $(U,X), (V,Y) \in \obj{\CC\times\DD}$, 
    $\mor{(U,X)}{(V,Y)}{\CC\times\DD} := \mor{U}{V}{\CC}\times\mor{X}{Y}{\DD}$.
  \end{enumerate}
\end{dfn}

\begin{prop}[Natural Transformations on Product Category]
  \link{nat_trans_prod_cat}
  
  Let $F, G : \map{\CC\times\DD}{\EE}{}{}$, 
  $(\al_{U,X}) \in \prod_{(U,X) \in \obj{\CC\times\DD}} 
    \mor{F(U,X)}{G(U,X)}{\EE}$.
  Then the following are equivalent. 
  \begin{enumerate}
    \item $\al : \map{F}{G}{}{}$.
    \item For all $(U,X) \in \obj{\CC\times\DD}$, 
    $\al_{U,-} : \map{F(U,-)}{G(U,-)}{}{}$ and 
    $\al_{-,X} : \map{F(-,X)}{G(-,X)}{}{}$.
  \end{enumerate}
\end{prop}
\begin{proof}
  Straight forward.
\end{proof}

\begin{dfn}[Adjunction]
  \link{adjunction}
  
  Let $R : \map{\CC}{\DD}{\CAT}{}$ and $L : \map{\DD}{\CC}{\CAT}{}$.
  We have the two functors 
  $\mor{L(\star)}{-}{\CC}, \mor{\star}{R(-)}{\DD} : 
  \map{\DD\op\times\CC}{\SET}{\CAT}{}$.
  Then $(L,R)$ is an \emph{adjunction} when 
  $\mor{L(\star)}{-}{\CC}, \mor{\star}{R(-)}{\DD}$
  are naturally isomorphic. 
  
  In this case, 
  $R$ is called the \emph{right adjoint of $L$}
  and $L$ is called the \emph{left adjoint of $R$}.
  The isomorphism is called the \emph{adjunction isomorphism}. 
  For all $f : \map{L(X)}{U}{\CC}{}$,
  the image of $f$ under the adjunction isomorphism is called 
  the \emph{adjunct of $f$}, denoted $f^\bot$. 
  Similarly for $g : \map{X}{R(U)}{\DD}{}$, 
  we have the \emph{adjunct of $g$}, denoted $g^\bot$.
\end{dfn}

\begin{prop}[Universal Morphism Characterisation of Adjunction]
  \link{uniprop_char_adj}{}

  Let $R : \map{\CC}{\DD}{\CAT}{}$.
  Then the following are equivalent : 
  \begin{enumerate}
    \item $R$ is a right adjoint. 
    \item There exists $L : \map{\DD}{\CC}{\CAT}{}$ such that 
    $(L,R)$ is an adjunction. 
  \end{enumerate}

  Dually, let $L : \map{\DD}{\CC}{\CAT}{}$.
  Then the following are equivalent : 
  \begin{enumerate}
    \item $L$ is a left adjoint. 
    \item There exists $R : \map{\CC}{\DD}{\CAT}{}$ such that 
    $(L,R)$ is an adjunction. 
  \end{enumerate}
\end{prop}
\begin{proof}
  $(\implies)$
  Let $R$ be a right adjoint, $L : \map{\obj{\DD}}{\obj{\CC}}{}{}$, 
  $\eta \in \Pi X \in \obj{\DD}, \mor{X}{RL(X)}{\DD}$,
  for all $X \in \obj{\DD}$, $(L(X),\eta(X))$ universal morphism from 
  $X$ to $R$.

  The universal properties at every $X \in \obj{\DD}$ implies 
  $L$ is functorial.
  By \hyperlink{uni_iff_rep}{universal iff represents},
  for all $X \in \obj{\DD}$, 
  we have $\mor{L(X)}{-}{\CC} \cong \mor{X}{R(-)}{\DD}$
  as functors $\map{\CC}{\SET}{}{}$.
  Let $f : \map{X}{Y}{\DD}{}$ and $U \in \obj{\CC}$.
  Then we have the following commutative diagram. 
  \begin{figure}[H]
    \centering
    \begin{tikzcd}
      \mor{L(X)}{U}{\CC} \ar[rrr,"R(-)\circ\eta(X)"]
      & & & \mor{X}{R(U)}{\DD} \\
      & g \circ L(f) \ar[r,mapsto]
      & R(g \circ L(f)) \circ \eta(X) = R(g) \circ \eta(Y) \circ f
      & \\
      & g \ar[u,mapsto] \ar[r,mapsto] & R(g)\circ\eta(Y) \ar[u,mapsto] & \\
      \mor{L(Y)}{U}{\CC} \ar[uuu,"(h^{L(f)})_U"]
        \ar[rrr,"R(-)\circ\eta(Y)"{swap}]
      & & & \mor{Y}{R(U)}{\DD} \ar[uuu,"(h^f)_U"{swap}]
    \end{tikzcd}
  \end{figure}
  Thus the isomorphism $\mor{L(X)}{-}{\CC} \cong \mor{X}{R(-)}{\DD}$
  is functorial in $X$, 
  and hence an isomorphism between
  $\mor{L(\star)}{-}{\CC} \cong \mor{\star}{R(-)}{\DD}$.

  $(\limplies)$ 
  Let $L : \map{\obj{\DD}}{\CC}{\CAT}{}$ such that 
  $(L,R)$ is an adjunction. 
  Then for each $X \in \obj{\DD}$, 
  $\mor{L(X)}{-}{\CC} \cong \mor{X}{R(-)}{\DD}$.
  Let $\eta(X)$ be the adjunct of $\id{L(X)}$.
  By \hyperlink{uni_iff_rep}{universal iff represents},
  $(L(X),\eta(X))$ is a universal morphism from $X$ to $R$.

  The dual has a similar argument. 
\end{proof}

\begin{prop}[Uniqueness of Adjoints]
  \link{adj_unique}{}

  Let $R, R_1 : \map{\CC}{\DD}{\CAT}{}$, $L, L_1: \map{\DD}{\CC}{\CAT}{}$.
  Then \begin{enumerate}
    \item If $(L,R)$ and $(L,R_1)$ are both adjunctions, 
    then $R \cong R_1$ as functors. 
    \item If $(L,R)$ and $(L_1, R)$ are both adjunctions, 
    then $L \cong L_1$ as functors. 
  \end{enumerate}
\end{prop}
\begin{proof}
  $(1)$ Let $(L,R), (L,R_1)$ both be adjunctions. 
  Let $f : \map{U}{V}{\CC}{}$. 
  We have an isomorphism between the functors 
  $\mor{-}{R(U)}{\DD}$ and $\mor{-}{R_1(U)}{\DD}$
  for all $U \in \obj{\CC}$. 
  By \hyperlink{yoneda}{Yoneda's lemma}, 
  these isomorphisms are equal to $h_{\al_U}$ 
  for some unique morphism $\al_U : \map{R(U)}{R_1(U)}{\DD}{}$.
  So we have the following commutative diagram. 
  \begin{figure}[H]
    \centering
    \begin{tikzcd}
      \mor{-}{R(U)}{\DD} \ar[r,"h_{\al_U}","\sim"{swap}] 
        \ar[d,"h_{R(f)}"{swap}]
      & \mor{-}{R_1(U)}{\DD} \ar[d,"h_{R_1(f)}"] \\
      \mor{-}{R(V)}{\DD} \ar[r,"h_{\al_V}"{swap},"\sim"] 
      & \mor{-}{R_1(V)}{\DD}
    \end{tikzcd}
  \end{figure}
  Again by Yoneda, 
  we have $R_1(f) \circ \al_U = \al_V \circ R(f)$.
  The fact that $h_{\al_U}$ is an isomorphism implies 
  $\al_U$ is an isomorphism. 
  Thus $\al$ is a natural isomorphism between $R, R_1$.

  $(2)$ Analogous. 
\end{proof}

\begin{rmk}
  There is another characterisation of adjunctions.
  This may be skipped on first reading since 
  in practice, the special case of Galois connection happens more often and 
  the proofs become much easier. 
\end{rmk}

\begin{prop}[Unit/Counit Characterisation of Adjunction]
  \link{unit_char_adj}{}
  
  Let $R : \map{\CC}{\DD}{\CAT}{}$ and $L : \map{\DD}{\CC}{\CAT}{}$.
  Then the following are equivalent : 
  \begin{enumerate}
    \item (Morphism Isomorphism) $(R,L)$ is an adjunction. 
    \item (Unit-Counit) 
    There exists $\eta : \map{\id{\DD}}{RL}{}{}$ and 
    $\ep : \map{LR}{\id{\CC}}{}{}$ such that 
    \begin{enumerate}
      \item $\id{L} = \ep L \circ L \eta$,
      that is to say for all $X \in \obj{D}$, 
      we have the following commutative diagram. 
      \begin{figure}[H]
        \centering
        \begin{tikzcd}
          L(X) \ar[rd,"\id{L(X)}"{swap}] \ar[r,"L(\eta(X))"]
          & LRL(X) \ar[d,"\ep(L(X))"] \\
          & L(X)
        \end{tikzcd}
      \end{figure}
      \item $\id{R} = R\ep \circ \eta R$, i.e. 
      for all $U \in \obj{\CC}$, 
      we have the following commutative diagram. 
      \begin{figure}[H]
        \centering
        \begin{tikzcd}
          R(U) \ar[rd,"\id{R(U)}"{swap}] \ar[r,"\eta(R(U))"] 
          & RLR(U) \ar[d,"R(\ep(U))"] \\
          & R(U) 
        \end{tikzcd}
      \end{figure}
    \end{enumerate}
    The above two equations are often called \emph{triangle-identities}.
  \end{enumerate}
\end{prop}
\begin{proof}
  $(1\implies 2)$
  For all $X \in \obj{\DD}$, 
  the adjunction isomorphism gives an isomorphism of functors
  \[
    \mor{L(X)}{-}{\CC} \iso \mor{X}{R(-)}{\DD}
  \]
  Define $\eta(X) := \id{L(X)}^\bot$. 
  Then by \hyperlink{uni_iff_rep}{universal iff represents}, 
  $(L(X),\eta(X))$ is a universal morphism from $X$ to $R$. 
  We claim that $\eta : \map{\id{\DD}}{RL}{}{}$. 

  Let $f : \map{X}{Y}{\DD}{}$. 
  Then by the universal property of $(L(X),\eta(X))$,
  we have the following commutative diagram. 
  \begin{figure}[H]
    \centering
    \begin{tikzcd}
      X \ar[r,"\eta(X)"] \ar[d,"f"{swap}] & RL(X) \ar[d,"RL(f)"] \\
      Y \ar[r,"\eta(Y)"{swap}] & RL(Y)
    \end{tikzcd}
  \end{figure}
  i.e. $\eta$ is a natural transformation as desired. 
  We similarly define $\ep(U) := \id{R(U)}^\bot$ for $U \in \obj{\CC}$
  and see that $\ep : \map{LR}{\id{\CC}}{}{}$. 

  To prove $(a)$, let $X \in \obj{\DD}$. 
  Then \begin{align*}
    \id{L(X)} 
    = \brkt{\id{L(X)}^\bot}^\bot 
    = \brkt{\eta(X)}^\bot 
    = \ep(L(X)) \circ L(\eta(X)) 
  \end{align*}
  where the last equality follows from 
  the universal property of $(RL(X),\ep(L(X)))$. 
  Similarly for $(b)$, we have for $U \in \obj{\CC}$, 
  \begin{align*}
    \id{R(U)} 
    = \brkt{\id{R(U)}^\bot}^\bot 
    = \brkt{\ep(U)}^\bot 
    = R(\ep(U)) \circ \eta(R(U))
  \end{align*}
  where the last equality is by
  the universal property of $(LR(U),\eta(R(U)))$.

  $(2\implies 1)$ 
  Let $(X,U)\in\obj{\DD\op \times \CC}$. 
  Since $(L(X),\eta(X))$ is supposed to be 
  a universal morphism from $X$ to $R$, 
  we define the adjunction map to be 
  \begin{align*}
    \mor{L(X)}{U}{\CC} &\overset{\bot}{\longleftrightarrow} 
    \mor{X}{R(U)}{\DD} \\
    f &\longmapsto R(f) \circ \eta(X) \\
    \ep(U) \circ L(g) &\longmapsfrom g
  \end{align*}
  Then for $f : \map{L(X)}{U}{\CC}{}$, 
  \begin{align*}
    \brkt{f^\bot}^\bot 
    &= \ep(U) \circ L(f^\bot) = \ep(U) \circ L\brkt{R(f) \circ \eta(X)} \\
    &= \ep(U) \circ LR(f) \circ L(\eta(X)) 
    = f \circ \ep(L(X)) \circ L(\eta(X)) = f
  \end{align*}
  Similarly, $\brkt{g^\bot}^\bot = g$.
  So $\bot$ is an isomorphism at all $(X,U)$.
  
  It remains to show naturality. 
  \hyperlink{nat_trans_prod_cat}{It suffices} to show that 
  the isomorphism is natural in both components. 
  Let $f : \map{X}{Y}{\DD\op}{}$. 
  Then we have the following diagram. 
  \begin{figure}[H]
    \centering
    \begin{tikzcd}
      \mor{L(X)}{U}{\CC} \ar[r,"\bot"] \ar[d,"h^{L(f)}"{swap}]
      & \mor{X}{R(U)}{\DD} \ar[d,"h^f"] \\
      \mor{L(Y)}{U}{\CC} \ar[r,"\bot"{swap}] & \mor{Y}{R(U)}{\DD}
    \end{tikzcd}
  \end{figure}
  It follows from $\eta : \map{\id{\DD}}{RL}{}{}$ that the above commutes.
  Similarly, naturality of $\ep$ implies naturality in the second component. 
  Hence $\bot$ is a natural isomorphism as desired. 
\end{proof}

\begin{rmk}
  The following is a special case of adjunction that is worth noting. 
\end{rmk}
\begin{dfn}[Galois Connection]
  
  Let $I, J$ be partially ordered sets. 
  Then $I, J$ can be seen as categories. 
  A \emph{monotone Galois connection between $I,J$} is 
  an adjunction between $I, J$.
  A \emph{antitone Galois connection between $I,J$} is 
  an adjunction between $I\op, J$. 
\end{dfn}
\begin{rmk}
  The \hyperlink{unit_char_adj}{unit/counit characterisation of adjunctions}
  shows that if $(R,L)$ is a Galois connection (mono or anti) between 
  partially ordered sets $I,J$, 
  then $R$ and $L$ are bijective on their images. 
\end{rmk}

\begin{dfn}[Free Functors]\link{free}
  
  Let $\CC$ be a subcategory of $\DD$ and 
  $L : \DD \to \CC$ be a functor. 
  Then $L$ is called a \emph{free functor from $\DD$ to $\CC$} when 
  it is left adjoint to the forgetful functor from $\CC$ to $\DD$. 
  Note that if it exists, $L$ is then unique up to natural isomorphism,
  so it is customary to called it \emph{the} free functor. 
\end{dfn}

\begin{eg}[Adjunctions]
  
  The adjunctions hinted at in \linkto{eg:functors}{section 2}.

  First, a list of free, forgetful adjunctions.
  \begin{itemize}
    \item (Free Group) 
    What we previously said about taking free groups is precisely 
    the a fact that it's a universal morphism from $S$ to the forgetful functor.
    The forgetful functor is a right adjoint.
    Its left adjoint is taking free groups. 
    \[
      \GRP(\<-\>,\star) \iso \SET(-,\star)
    \]
    \item (Free Left Module over a Ring) Similarly, 
    for a ring $R$, 
    taking free left modules over a set is a left adjoint to forgetful 
    $R\MOD \to \SET$. 
    \[
      R\MOD(R^{\oplus(-)},\star) \iso \SET(-,\star)
    \]
    \item (Free Commutative Algebra over a Ring)
    For a commutative ring $K$, \[
      \CALG(K)(K[-],\star) \iso \SET(-,\star)
    \]
    \item (Extension and Contraction of Scalars)
    Let $B$ be a commutative algebra over $A$ 
    ($A$ is commutative by definition).
    Then extension of scalars is the free functor left adjoint to
    the forgetful $B\MOD \to A\MOD$. \[
      B\MOD((-) \otimes_A B, \star) \iso A\MOD(-,\star)
    \]
    \item (Localization of Modules)
    Let $A$ be a commutative ring and $S \subs A$ a multiplicative set. 
    Then localization with respect to $S$ is the free functor
    left adjoint to the forgetful $S\inv A \MOD \to A\MOD$. \[
      S\inv A\MOD(S\inv(-), \star) \iso A\MOD(-,\star)
    \]
    Note that by \linkto{adj_unique}{uniqueness of adjoints},
    this can be seen as a special case of extension and contraction of scalars
    via the commutative $A$-algebra $S\inv A$.

    \item (Symmetric Algebra)
    Let $A$ be a commutative ring. 
    Then taking symmetric algebas of modules is the free functor 
    left adjoint to the forgetful $\CALG(A) \to A\MOD$.
    \[
      \CALG(A)(Symm(-),\star) \iso A\MOD(-,\star)
    \]

    \item (Discrete Topology)
    Giving sets the discrete topology is the free functor left adjoint to 
    the forgetful $\TOP \to \SET$. 
    \[
      \TOP((-,2^-),\star) \iso \SET(-,\star)
    \]

    \item (Free Category on a Pre-Ordered Set)
    As \linkto{eg:cat_ord}{previously discuessed},
    every pre-ordered set can be made into a category by considering 
    the relation $\leq$ as morphisms. 
    This is the free functor left adjoint to the forgetful 
    $\CAT \to \ORD$, where we see any category $\CC$ as a pre-ordered set by
    declaring for $U, V \in \obj{\CC}$, $U \leq V := \CC(U,V) \neq \nothing$.

  \end{itemize}

  A list of adjunctions, 
  themed ``moving structures on objects across morphisms''. 
  \begin{itemize}
    \item (Image, Preimage of ``Substructures'')
    Let $f : U \to V$ be a morphism of sets. 
    Then \[
      2^U(-,f\inv(\star)) \iso 2^V(f(-),\star)
    \]
    If $f$ is instead a morphism of groups,
    then this upgrades to \[
      \mathbf{Sub}\GRP(U)(-,f\inv(\star)) \iso 
      \mathbf{Sub}\GRP(V)(f(-),\star)
    \]
    If $f$ is instead a morphism of rings, 
    \[
      \mathbf{Sub}\RING(U)(-,f\inv(\star)) \iso 
      \mathbf{Sub}\RING(V)(f(-),\star)
    \]
    If $f$ is instead a morphism of left $R$-modules for some 
    ring $R$, \[
      \mathbf{Sub}R\MOD(U)(-,f\inv(\star)) \iso
      \mathbf{Sub}R\MOD(V)(f(-),\star)
    \]
    If $f$ is instead a morphism of $K$-algebras for some commutative ring $K$,
    \[
      \mathbf{Sub}K\ALG(U)(-,f\inv(\star)) \iso 
      \mathbf{Sub}K\ALG(V)(f(-),\star)
    \]
    \item (Image, Preimage of Filters)
    Let $f : U \to V$ be a morphism of sets. 
    Then \[
      \fil(U)(-,{f}\inv(\star)) \iso \fil(V)(f_{\fil}(-),\star)
    \]
    where for a filter $F$ on $U$,
    $f_{\fil}(F) := \set{W \subs V \st f\inv W \in F}$.
  \end{itemize}

  % Given a category $\CC$ with finite products,
  % for a fixed $Y \in \obj{\CC}$, 
  % $(-)\times Y : \CC \to \CC$ is functorial. 
  % Fixing another $Z \in \obj{\CC}$,
  % an \emph{exponential object} $(Z^Y,ev)$ is a universal morphism 
  % from $(-)\times Y$ to $Z$.
  The following is a list of instances of ``exponential objects''.
  \begin{itemize}
    \item Let $Y$ be a set. 
    Taking the cartesian product with $Y$, 
    $(-)\times Y : \SET \to \SET$, is functorial.
    Then we have the adjunction between $(-)\times Y$ and $h^Y$ : 
    \[
      \SET((-)\times Y, \star) \iso \SET(-, \SET(Y, \star))
    \]
    \item Let $N$ be an $A$-module where $A$ is a commutative ring. 
    Then $(-) \otimes_A N : A\MOD \to A\MOD$ is functorial.
    On the other hand, the coYoneda embedding $h^N$ of $N$ is naturally 
    a functor $A\MOD \to A\MOD$. 
    Then we have the adjunction between $(-)\otimes_A N$ and $h^N$ : 
    \[
      A\MOD((-)\otimes_A N, \star) \iso A\MOD(-,h^N(\star))
    \]
    \item Let $\DD$ be a category. 
    Then taking the product of categories with $\DD$ yields a 
    functor $(-) \times \DD : \CAT \to \CAT$.
    On the other hand, the coYoneda embedding of $\DD$ is naturally a functor
    $h^\DD : \CAT \to \CAT$. 
    Then we have the adjunction : \[
      \CAT((-)\times \DD, \star) \iso \CAT(-,h^\DD(\star))
    \]
  \end{itemize}

  (TODO : Add to this list)

\end{eg}